Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-23 introduction.tex
Reworded galaxy catalog sentene
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1151 ccdd05d5-56c1-461a-bf98-85f6876523b4

It is infeasible to search hundreds of square degrees for a prompt
counterpart. For
reference, \textsc{lsst} should see first light around the same time as
Advanced \LIGO{} and will have an unparalleled field of view of 9.6 deg$^2$
\citep{2008arXiv0805.2366I}.  However, if we can take galactic luminosities
to accurately reflect mass and thus be a proxy for the \CBC{} event rate, it is
possible to reduce the localization uncertainty using a galaxy catalog, along
with the sky location and luminosity distance estimate from the \GW{} signal,
as a prior probability distribution \citep{galaxy-catalog} as was done in
S6/VSR3. Within the expected Advanced \LIGO{} \textsc{ns}--\textsc{ns} horizon
distance, the number of galaxies that can produce a given signal
amplitude is much larger than the number for initial \LIGO{} and thus the
catalog will not be as useful for downselecting pointings generally. However,
our exceptional sources will necessarily be extremely nearby. Within this
reduced volume there will be fewer galaxies to consider for a given
candidate and catalog completeness will be less of a concern.
This should allow us to shrink the 90\% confidence area substantially.

>>>>

It is infeasible to search hundreds of square degrees for a prompt
counterpart. For
reference, \textsc{lsst} should see first light around the same time as
Advanced \LIGO{} and will have an unparalleled field of view of 9.6 deg$^2$
\citep{2008arXiv0805.2366I}.  However, if we can take galactic luminosities
to accurately reflect mass and thus be a proxy for the \CBC{} event rate, it is
possible to reduce the localization uncertainty by only looking at galaxies from a
catalog that lie near the sky location and luminosity distance estimate from the \GW{}
signal~\citep{galaxy-catalog} as was done in S6/VSR3.
Within the expected Advanced \LIGO{} \textsc{ns}--\textsc{ns} horizon
distance, the number of galaxies that can produce a given signal
amplitude is much larger than the number for initial \LIGO{} and thus the
catalog will not be as useful for downselecting pointings generally. However,
our exceptional sources will necessarily be extremely nearby. Within this
reduced volume there will be fewer galaxies to consider for a given
candidate and catalog completeness will be less of a concern.
This should allow us to shrink the 90\% confidence area substantially.
